The Feasibility of Stylometry as a Service

### 2013-12-09 paper/paper.tex
Add deploy info

>>>>

\section{Deployment}

The web application can be deployed via the following commands on a
Ubuntu 12.04 desktop installation:

sudo apt-get update
sudo apt-get install ubuntu-desktop ant openjdk-7-jdk postgresql git
sudo add-apt-repository ppa:chris-lea/node.js
sudo apt-get update
sudo apt-get install nodejs

# Clone Repository

git clone https://github.com/LRParser/anonymouth.git

# Start service
cd anonymouth
./bootstrap.sh
